\documentclass[10pt, letterpaper]{article}
\usepackage[margin=0.7in]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{xcolor}
\usepackage{fontawesome5}

% Define Theme Color (Gold/Tan)
\definecolor{theme_gold}{HTML}{b3a482}

\urlstyle{same}

% Section Styling
\titleformat{\section}{\large\bfseries\color{theme_gold}}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{12pt}{8pt}

\begin{document}

% --- HEADER ---
\begin{center}
    {\Huge \textbf{Hadi Fathipour}} \\
    \vspace{4pt}
    {\large ML and Backend Developer | Data Analyst} \\
    \vspace{6pt}
    \small
    \faEnvelope\ \href{mailto:hadifathi13781378@gmail.com}{hadifathi13781378@gmail.com} \quad
    \faPhone\ +98 921 8284 877 \\
    \faLinkedin\ \href{https://linkedin.com/in/hadi-fathipour-8b39071a2}{linkedin.com/in/hadi-fathipour-8b39071a2} \quad
    \faGithub\ \href{https://github.com/hadif1999}{github.com/hadif1999}
\end{center}

% --- PROFESSIONAL SUMMARY ---
\section{Professional Summary}
I am an enthusiastic, self-motivated developer with strong analytical and problem-solving skills.
My technical expertise spans Machine Learning, Backend development, and Data Analysis.
I have a robust background in Robotics and autonomous systems, including control engineering, embedded systems programming, and advanced numerical simulations.
I am a lifelong learner who thrives on analyzing real-world problems and finding unique solutions through creativity and knowledge.

% --- TECHNICAL TOOLS & TECHNOLOGIES ---
\section{Technical Expertise}
\begin{itemize}[leftmargin=*, noitemsep]
    \item \textbf{Programming Languages:} Python (NumPy, Pandas), MATLAB, C++ (Arduino), SQL, HTML/CSS
    \item \textbf{Machine Learning \& AI:} TensorFlow, Keras, scikit-learn, Deep Learning, Time-series Forecasting (TFT, Transformers, RNN, ARIMA), BERT, XGBoost, SVM
    \item \textbf{Backend \& DevOps:} FastAPI, Docker, Docker-py, Celery, Linux, Git, REST API
    \item \textbf{Data \& Databases:} MySQL, SQLModel, SQLAlchemy, Market Data Analysis
\end{itemize}

% --- PROFESSIONAL EXPERIENCE ---
\section{Experience}

\textbf{Freelance ML Engineer and Data Analyst} \hfill 2021 -- Present \\
\begin{itemize}[leftmargin=*, noitemsep]
    \item Completed various projects in natural language processing, data analysis, business analysis, and computer vision.
    \item Sourced and delivered technical solutions through platforms including LinkedIn, Upwork, and Freelancer.com.
    \item Developed standalone applications to automate data processing and strategic decision-making.
\end{itemize}

\vspace{5pt}

\textbf{Algorithmic Trader} \hfill 2022 -- Present \\
\begin{itemize}[leftmargin=*, noitemsep]
    \item Developed and deployed custom trading strategies and market data analysis tools for cryptocurrency markets.
    \item Engineered algorithmic trading bots as Docker containers to run as standalone applications on servers.
    \item Utilized advanced time-series analysis models (Transformers, RNNs, ARIMA) for market prediction.
\end{itemize}

\newpage % PAGE 2

% --- KEY PROJECTS ---
\section{Key Projects}

\textbf{Urban Drone Backend \& AI Control System} \\
\textit{Tools: FastAPI, AsyncIO, NetworkX, GeoPandas, Shapely, GeoPy, MAVSDK, PyMAVLink}
\begin{itemize}[leftmargin=*, noitemsep]
    \item Developed AI-driven backend systems to autonomously customize urban drone behavior and dynamically avoid restricted zones using graph-based A* path planning.
    \item Implemented high-performance, fully asynchronous backend services and real-time dashboard panels to manage fleets of urban drones and monitor live telemetry and status.
    \item Designed geospatial processing pipelines for urban environments using GeoPandas, Shapely, and GeoPy for accurate navigation and constraint enforcement.
    \item Built drone communication layers using MAVSDK and PyMAVLink to enable reliable real-time command and control.
\end{itemize}

\vspace{5pt}

\textbf{IFUND: Prop-Trading Platform Backend \& Infrastructure} \\
\textit{Tools: FastAPI, Docker, Docker-py, Python}
\begin{itemize}[leftmargin=*, noitemsep]
    \item Designed and implemented a backend API to systematically create, configure, and manage customized MetaTrader 5 Docker containers for prop-trading challenges.
    \item Developed container lifecycle management features, including provisioning, editing, isolation, and removal through RESTful endpoints.
    \item Built a standalone MetaTrader 5 Docker image to enable large-scale deployment of trading bots and prop-trading platforms without local MT5 installations.
    \item Supported scalable trading infrastructure used in real-world prop-trading environments.
\end{itemize}
\textit{Platform:} \href{https://panel.ifund.trade/login}{panel.ifund.trade} \quad
\textit{Docker Image:} \href{https://hub.docker.com/r/hadi1999/meta5_custom_minimal}{Docker Hub}

\vspace{5pt}

\textbf{TONPAY: Telegram Crypto Wallet (TON Blockchain)} \\
\textit{Tools: SQLModel, SQLAlchemy, AsyncIO, python-telegram-bot}
\begin{itemize}[leftmargin=*, noitemsep]
    \item Designed and implemented a fully asynchronous cryptocurrency wallet for the TON blockchain as a Telegram bot.
    \item Built scalable database architectures supporting multiple wallets per user using SQLModel and SQLAlchemy.
    \item Implemented wallet management, asset transfers, and user isolation within an async event-driven system.
\end{itemize}
\textit{Repository:} \href{https://github.com/hadif1999/tonpay}{github.com/hadif1999/tonpay}

\vspace{5pt}

\textbf{Pycoin: Algorithmic Trading Python Framework} \\
\textit{Tools: Python, Binance API, BingX, KuCoin}
\begin{itemize}[leftmargin=*, noitemsep]
    \item Developed an open-source Python framework for historical market data retrieval and technical analysis across multiple cryptocurrency exchanges.
    \item Implemented tools for trend detection, high-low identification, probabilistic market analysis, and strategy development.
    \item Enabled rapid development of indicator-based and price-action trading strategies for algorithmic trading systems.
\end{itemize}
\textit{Repository:} \href{https://github.com/hadif1999/pycoin}{github.com/hadif1999/pycoin}


% --- ACADEMIC PROJECTS & RESEARCH ---
\section{Academic \& Robotics Projects}

\textbf{Reaction Wheel Inverted Pendulum (Bachelor Project)} \\
\textit{Tools: MATLAB, Arduino, C++, PID, LQR}
\begin{itemize}[leftmargin=*, noitemsep]
    \item Designed and simulated a reaction wheel inverted pendulum for satellite feasibility testing.
    \item Implemented real-time control algorithms (PID and LQR) using C++ on Arduino hardware.
\end{itemize}

\vspace{5pt}

\textbf{IOT Smoke Detection System} \\
\textit{Tools: Neural Networks, IOT Sensors}
\begin{itemize}[leftmargin=*, noitemsep]
    \item Built a fire prediction model using pressure, humidity, and gas sensor data.
    \item Achieved 93\% prediction accuracy using a neural network architecture.
\end{itemize}

% --- EDUCATION ---
\section{Education}
\textbf{KNTU University} | Bachelor of Engineering | GPA: 3.81 \hfill 2017 -- 2022 \\
\textbf{Amir Kabir University (Polytechnic)} | Master's degree (Withdrawal) \hfill 2022

% --- HOBBIES ---
\section{Hobbies}
Mountain climbing, gym, swimming, reading, and watching movies.

\end{document}
