\documentclass[10pt, letterpaper]{article}

\usepackage[margin=0.7in]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{xcolor}
\usepackage{fontawesome5}
\usepackage[none]{hyphenat}
\usepackage{tabularx}
\usepackage{array}
\usepackage{microtype}

% Theme color (Gold/Tan)
\definecolor{theme_gold}{HTML}{b3a482}

\urlstyle{same}
\setlength{\parindent}{0pt}
\pagenumbering{gobble}

% Slightly tighter, cleaner spacing
\setlength{\parskip}{2pt}

% Bullet + list spacing tuned for resume
\setlist[itemize]{
  leftmargin=*,
  noitemsep,
  topsep=2pt,
  parsep=0pt,
  partopsep=0pt
}
\renewcommand\labelitemi{\small\textbullet}

% Section styling (cleaner + slightly tighter)
\titleformat{\section}{\large\bfseries\color{theme_gold}}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{10pt}{6pt}

% Helper: consistent entry header
\newcommand{\entry}[4]{%
  \begin{tabularx}{\textwidth}{@{}X r@{}}
    \textbf{#1} — #2 & \textit{#3} \\
    \textit{#4} & \\
  \end{tabularx}
}

% Helper: project header
\newcommand{\project}[2]{%
  \textbf{#1}\\
  \textit{Tools: #2}
}

\begin{document}

% --- HEADER (clean, aligned) ---
\begin{center}
  {\Huge \textbf{Hadi Fathipour}}\\[-2pt]
  {\large Backend \& AI Engineer}\\[6pt]

  \small
  \begin{tabularx}{0.92\textwidth}{@{}X X@{}}
    \faEnvelope\ \href{mailto:hadifathi13781378@gmail.com}{hadifathi13781378@gmail.com} &
    \faPhone\ +98 921 8284 877 \\
    \faLinkedin\ \href{https://linkedin.com/in/hadi-fathipour-8b39071a2}{linkedin.com/in/hadi-fathipour-8b39071a2} &
    \faGithub\ \href{https://github.com/hadif1999}{github.com/hadif1999}
  \end{tabularx}
\end{center}

% --- SUMMARY ---
\section{Professional Summary}
Backend \& AI engineer with experience building high-performance, asynchronous backend systems and real-time APIs for production environments.
Strong background in machine learning, data analysis, and autonomous systems, with a focus on scalable architecture, intelligent data processing, and automation.
Proven ability to translate complex domain and business requirements into reliable backend services operating in real-world conditions.

% --- SKILLS (more readable) ---
\section{Technical Expertise}
\begin{itemize}
  \item \textbf{Programming:} Python (NumPy, Pandas), SQL, C++ (Arduino), MATLAB, HTML/CSS
  \item \textbf{Backend \& DevOps:} FastAPI, Docker, Docker-py, Celery, Linux, Git, REST, WebSockets, gRPC
  \item \textbf{ML \& AI:} TensorFlow, Keras, scikit-learn, Transformers, BERT, XGBoost, SVM, RNN, ARIMA, time-series forecasting
  \item \textbf{Data \& DB:} MySQL, SQLAlchemy, SQLModel, market data analysis
\end{itemize}

% --- EXPERIENCE (consistent, polished headers) ---
\section{Experience}

\entry{Backend \& AI Developer}{Sanam.pro (RobTK)}{Moscow, Russia}{2025 -- 2026}
\begin{itemize}
  \item Designed and implemented a high-performance, fully asynchronous backend for real-time drone command and telemetry management using FastAPI.
  \item Built secure, role-based authentication for operators and administrators to control access to drone APIs and monitoring services.
  \item Developed AI-driven geospatial monitoring to prevent drones from entering restricted zones using graph-based path planning.
  \item Implemented path-planning algorithms with NetworkX and optimized geo-computation pipelines using Shapely, GeoPandas, GeoPy, and Cython.
  \item Integrated MAVSDK and PyMAVLink for reliable real-time command and data exchange.
\end{itemize}

\vspace{6pt}

\entry{Freelance ML \& Backend Engineer}{Self-employed}{Remote}{2021 -- Present}
\begin{itemize}
  \item Delivered end-to-end ML and backend solutions across NLP, time-series analysis, business intelligence, and computer vision.
  \item Designed and deployed production-ready APIs and data pipelines to automate analytics and decision-making workflows for multiple clients.
  \item Collaborated with global clients via LinkedIn, Upwork, and Freelancer to translate requirements into scalable technical solutions.
\end{itemize}

\vspace{6pt}

\entry{Algorithmic Trader \& Systems Developer}{Self-employed}{Remote}{2022 -- Present}
\begin{itemize}
  \item Designed and deployed algorithmic trading systems and data analysis pipelines for cryptocurrency markets.
  \item Built containerized execution services using Docker for reliable unattended operation on servers.
  \item Applied forecasting techniques (Transformers, RNNs, ARIMA) to model market behavior and evaluate strategy performance.
\end{itemize}

% --- PROJECTS (cleaner spacing + consistent headers) ---
\section{Key Projects}

\project{Urban Drone Backend \& AI Control System}{FastAPI, AsyncIO, NetworkX, GeoPandas, Shapely, GeoPy, MAVSDK, PyMAVLink}
\begin{itemize}
  \item Developed AI-driven backend systems to customize urban drone behavior and avoid restricted zones using A* path planning.
  \item Built fully asynchronous services and real-time dashboard panels to manage fleets and monitor live telemetry.
  \item Implemented geospatial processing for urban constraints and navigation enforcement.
\end{itemize}

\vspace{6pt}

\project{IFUND: Prop-Trading Platform Backend \& Infrastructure}{FastAPI, Docker, Docker-py, Python}
\begin{itemize}
  \item Built an API to create, configure, and manage customized MetaTrader 5 Docker containers for prop-trading challenges.
  \item Implemented container lifecycle operations (provisioning, editing, isolation, removal) via REST endpoints.
  \item Developed a standalone MT5 Docker image to support large-scale deployment without local installations.
\end{itemize}
\textit{Platform:} \href{https://panel.ifund.trade/login}{panel.ifund.trade} \quad
\textit{Docker Image:} \href{https://hub.docker.com/r/hadi1999/meta5_custom_minimal}{Docker Hub}

\vspace{6pt}

\project{TONPAY: Telegram Crypto Wallet (TON Blockchain)}{SQLModel, SQLAlchemy, AsyncIO, python-telegram-bot}
\begin{itemize}
  \item Designed a fully asynchronous cryptocurrency wallet as a Telegram bot for the TON blockchain.
  \item Built scalable database models supporting multiple wallets per user with isolation and transfer flows.
\end{itemize}
\textit{Repository:} \href{https://github.com/hadif1999/tonpay}{github.com/hadif1999/tonpay}

\vspace{6pt}

\project{Pycoin: Algorithmic Trading Python Framework}{Python, Binance API, BingX, KuCoin}
\begin{itemize}
  \item Developed an open-source framework for historical market data retrieval and technical analysis across exchanges.
  \item Implemented tools for trend detection, high-low identification, probabilistic analysis, and strategy development.
\end{itemize}
\textit{Repository:} \href{https://github.com/hadif1999/pycoin}{github.com/hadif1999/pycoin}

% --- EDUCATION (aligned, clean) ---
\section{Education}
\begin{tabularx}{\textwidth}{@{}X r@{}}
  \textbf{KNTU University of Technology} — Bachelor of Engineering (GPA: 3.81) & 2017 -- 2022 \\
  \textbf{KNTU University of Technology} — M.Sc. Computer Engineering (Artificial Intelligence) & 2026 -- Present \\
\end{tabularx}

% --- HOBBIES (optional) ---
\section{Hobbies}
Mountain climbing, gym, swimming, reading, and watching movies.

\end{document}
