\documentclass[10pt, letterpaper]{article}
\usepackage[margin=0.7in]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{xcolor}
\usepackage{fontawesome5}
\usepackage[none]{hyphenat} % <-- FIX 1: disable hyphenation

% Define Theme Color (Gold/Tan)
\definecolor{theme_gold}{HTML}{b3a482}

\urlstyle{same}

% Section Styling
\titleformat{\section}{\large\bfseries\color{theme_gold}}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{12pt}{8pt}
\setlength{\parindent}{0pt}

\begin{document}

% --- HEADER ---
\begin{center}
    {\Huge \textbf{Hadi Fathipour}} \\
    \vspace{4pt}
    {\large Backend \& AI Engineer} \\
    \vspace{6pt}
    \small
    \faEnvelope\ \href{mailto:hadifathi13781378@gmail.com}{hadifathi13781378@gmail.com} \quad
    \faPhone\ +98 921 8284 877 \\
    \faLinkedin\ \href{https://linkedin.com/in/hadi-fathipour-8b39071a2}{linkedin.com/in/hadi-fathipour-8b39071a2} \quad
    \faGithub\ \href{https://github.com/hadif1999}{github.com/hadif1999}
\end{center}

% --- PROFESSIONAL SUMMARY ---
\section{Professional Summary}
Backend \& AI engineer with experience building high-performance, asynchronous backend systems and real-time APIs for production environments.
Strong background in machine learning, data analysis, and autonomous systems, with a focus on scalable architecture, intelligent data processing, and automation.
Proven ability to translate complex domain and business requirements into reliable backend services operating in real-world conditions.

% --- TECHNICAL TOOLS & TECHNOLOGIES ---
\section{Technical Expertise}
\begin{itemize}[leftmargin=*, noitemsep]
    \item \textbf{Programming Languages:} Python (NumPy, Pandas), MATLAB, C++ (Arduino), SQL, HTML/CSS
    \item \textbf{Machine Learning \& AI:} TensorFlow, Keras, scikit-learn, Deep Learning, Time-series Forecasting, Transformers, RNN, ARIMA, BERT, XGBoost, SVM
    \item \textbf{Backend \& DevOps:} FastAPI, Docker, Docker-py, Celery, Linux, Git, REST API, Websockets, GRPC
    \item \textbf{Data \& Databases:} MySQL, SQLModel, SQLAlchemy, Market Data Analysis
\end{itemize}

% --- PROFESSIONAL EXPERIENCE ---
\section{Experience}

\textbf{Backend \& AI Developer} — Sanam.pro (RobTK) \hfill Moscow, Russia \\
\textit{2025 -- 2026}
\begin{itemize}[leftmargin=*, noitemsep]
    \item Designed and implemented a high-performance, fully asynchronous backend system for real-time drone command and telemetry management using FastAPI.
    \item Built secure, role-based authentication systems for operators and administrators, enabling controlled access to drone APIs and monitoring services.
    \item Developed AI-driven geospatial monitoring systems to autonomously prevent drones from entering restricted zones using graph-based path planning.
    \item Implemented advanced path-planning algorithms leveraging NetworkX and optimized geo-computation pipelines using Shapely, GeoPandas, GeoPy, and Cython.
    \item Integrated real-time drone communication layers using MAVSDK and PyMAVLink for reliable command and data exchange.
\end{itemize}

\vspace{8pt}

\textbf{Freelance ML \& Backend Engineer} — Self-employed \hfill Remote \\
\textit{2021 -- Present}
\begin{itemize}[leftmargin=*, noitemsep]
    \item Delivered end-to-end ML and backend solutions across NLP, time-series analysis, business intelligence, and computer vision domains.
    \item Designed and deployed production-ready APIs and data pipelines to automate analytics and decision-making workflows for multiple clients.
    \item Collaborated with global clients through platforms such as LinkedIn, Upwork, and Freelancer, translating business requirements into scalable technical solutions.
\end{itemize}

\vspace{8pt}

\textbf{Algorithmic Trader \& Systems Developer} — Self-employed \hfill Remote \\
\textit{2022 -- Present}
\begin{itemize}[leftmargin=*, noitemsep]
    \item Designed and deployed algorithmic trading systems and data analysis pipelines for cryptocurrency markets.
    \item Built containerized trading bots and execution services using Docker to enable reliable, unattended operation on cloud servers.
    \item Applied advanced time-series forecasting techniques, including Transformers, RNNs, and ARIMA, to model market behavior and strategy performance.
\end{itemize}

\newpage % page 2

% --- KEY PROJECTS ---
\section{Key Projects}

\textbf{Urban Drone Backend \& AI Control System} \\
\textit{Tools: FastAPI, AsyncIO, NetworkX, GeoPandas, Shapely, GeoPy, MAVSDK, PyMAVLink}
\begin{itemize}[leftmargin=*, noitemsep]
    \item Developed AI-driven backend systems to autonomously customize urban drone behavior and dynamically avoid restricted zones using graph-based A* path planning.
    \item Implemented high-performance, fully asynchronous backend services and real-time dashboard panels to manage fleets of urban drones and monitor live telemetry and status.
    \item Designed geospatial processing pipelines for urban environments using GeoPandas, Shapely, and GeoPy for accurate navigation and constraint enforcement.
    \item Built drone communication layers using MAVSDK and PyMAVLink to enable reliable real-time command and control.
\end{itemize}

\vspace{10pt}

\textbf{IFUND: Prop-Trading Platform Backend \& Infrastructure} \\
\textit{Tools: FastAPI, Docker, Docker-py, Python}
\begin{itemize}[leftmargin=*, noitemsep]
    \item Designed and implemented a backend API to systematically create, configure, and manage customized MetaTrader 5 Docker containers for prop-trading challenges.
    \item Developed container lifecycle management features, including provisioning, editing, isolation, and removal through RESTful endpoints.
    \item Built a standalone MetaTrader 5 Docker image to enable large-scale deployment of trading bots and prop-trading platforms without local MT5 installations.
    \item Supported scalable trading infrastructure used in real-world prop-trading environments.
\end{itemize}
\textit{Platform:} \href{https://panel.ifund.trade/login}{panel.ifund.trade} \quad
\textit{Docker Image:} \href{https://hub.docker.com/r/hadi1999/meta5_custom_minimal}{Docker Hub}

\vspace{10pt}

\textbf{TONPAY: Telegram Crypto Wallet (TON Blockchain)} \\
\textit{Tools: SQLModel, SQLAlchemy, AsyncIO, python-telegram-bot}
\begin{itemize}[leftmargin=*, noitemsep]
    \item Designed and implemented a fully asynchronous cryptocurrency wallet for the TON blockchain as a Telegram bot.
    \item Built scalable database architectures supporting multiple wallets per user using SQLModel and SQLAlchemy.
    \item Implemented wallet management, asset transfers, and user isolation within an async event-driven system.
\end{itemize}
\textit{Repository:} \href{https://github.com/hadif1999/tonpay}{github.com/hadif1999/tonpay}

\vspace{10pt}

\textbf{Pycoin: Algorithmic Trading Python Framework} \\
\textit{Tools: Python, Binance API, BingX, KuCoin}
\begin{itemize}[leftmargin=*, noitemsep]
    \item Developed an open-source Python framework for historical market data retrieval and technical analysis across multiple cryptocurrency exchanges.
    \item Implemented tools for trend detection, high-low identification, probabilistic market analysis, and strategy development.
    \item Enabled rapid development of indicator-based and price-action trading strategies for algorithmic trading systems.
\end{itemize}
\textit{Repository:} \href{https://github.com/hadif1999/pycoin}{github.com/hadif1999/pycoin}

% --- EDUCATION ---
\section{Education}
\textbf{KNTU University of Technology} | Bachelor of Engineering | GPA: 3.81 \hfill 2017 -- 2022 \par
\textbf{KNTU University of Technology} | M.Sc. Computer Engineering (Artificial Intelligence) \hfill 2026 -- Present

% --- HOBBIES ---
\section{Hobbies}
Mountain climbing, gym, swimming, reading, and watching movies.

\end{document}
